\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-21 paper.qmd
Commet unnecessary code chunks

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"}
![](figures/scurve/sc_best_trimesh.png)

![](figures/scurve/sc_1.png)

![](figures/scurve/sc_2.png)

![](figures/scurve/sc_3.png)

XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>). 
:::

@@

```{r}
#| echo: false
#| label: fig-lg-scurve
#| fig-pos: H
#| fig-cap: "$2\\text{-}D$ model generated for different benchmark values to remove long edges: (a) benchmark = $0.201$ (default), (b) benchmark = $0.35$, and (c) benchmark = $1.1$. What is the effective benchmark value to remove long edges?"
#| fig-width: 6
#| fig-height: 3

@@

@fig-scurve-sc-best shows one of the best fits for S-curve data. TriMAP with $15$ nearest neighbors for forming the nearest neighbor triplet (`n_inliers`), $3$ outliers for forming the nearest neighbor triplets (`n_outliers`), $3$ random triplets per point (`n_random`) is used as the NLDR method. The model is generated with $103$ bins, which have a width of $0.154$ and a height of $0.133$. Edges with lengths greater than $0.266$ are removed.

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc-best layout-ncol="4" fig-pos="H"}
![](figures/scurve/sc_best_trimap_trimesh.png)

![](figures/scurve/sc_trimap_best_1.png)

![](figures/scurve/sc_trimap_best_2.png)

![](figures/scurve/sc_trimap_best_3.png)

Model in \gD{}, on the TriMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has twists. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/zEz2MUCtADM>). 
:::

>>>>

<!--langevitour with pD model for S-curve-->
<!-- ::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_best_trimesh.png) -->

<!-- ![](figures/scurve/sc_1.png) -->

<!-- ![](figures/scurve/sc_2.png) -->

<!-- ![](figures/scurve/sc_3.png) -->

<!-- XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>).  -->
<!-- ::: -->

@@

```{r}
#| echo: false
#| label: fig-lg-scurve
#| fig-pos: H
#| fig-cap: "$2\\text{-}D$ model generated for different benchmark values to remove long edges: (a) benchmark = $0.201$ (default), (b) benchmark = $0.35$, and (c) benchmark = $1.1$. What is the effective benchmark value to remove long edges?"
#| fig-width: 6
#| fig-height: 3
#| eval: false

@@

<!-- @fig-scurve-sc-best shows one of the best fits for S-curve data. TriMAP with $15$ nearest neighbors for forming the nearest neighbor triplet (`n_inliers`), $3$ outliers for forming the nearest neighbor triplets (`n_outliers`), $3$ random triplets per point (`n_random`) is used as the NLDR method. The model is generated with $103$ bins, which have a width of $0.154$ and a height of $0.133$. Edges with lengths greater than $0.266$ are removed.  -->

<!--langevitour with pD model for S-curve--> 
<!-- ::: {#fig-scurve-sc-best layout-ncol="4" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_best_trimap_trimesh.png) -->

<!-- ![](figures/scurve/sc_trimap_best_1.png) -->

<!-- ![](figures/scurve/sc_trimap_best_2.png) -->

<!-- ![](figures/scurve/sc_trimap_best_3.png) -->

<!-- Model in \gD{}, on the TriMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has twists. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/zEz2MUCtADM>).  -->
<!-- ::: -->

### 2024-07-21 paper.tex
Added new data with new S-curve data generation
Commet unnecessary code chunks

\caption{\label{fig-scurve-true-sc}Three views of the true model in
projections from \(7\text{-}D\), for the S-curve data. The model closely
fits the shape. (The \textbf{langevitour} software is used to view the
data with a tour, and the full video is available at
(\url{https://youtu.be/tYATMiSlCXQ}).}

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_best_trimesh.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}XXX Model in \gD{}, on the UMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has breaks which
means that it does not adequately capture the surface. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \url{https://youtu.be/N6iWEj3aVps}).}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-lg-scurve-1.pdf}

\caption{\label{fig-lg-scurve}\(2\text{-}D\) model generated for
different benchmark values to remove long edges: (a) benchmark =
\(0.201\) (default), (b) benchmark = \(0.35\), and (c) benchmark =
\(1.1\). What is the effective benchmark value to remove long edges?}

@@

Figure~\ref{fig-scurve-sc-best} shows one of the best fits for S-curve
data. TriMAP with \(15\) nearest neighbors for forming the nearest
neighbor triplet (\texttt{n\_inliers}), \(3\) outliers for forming the
nearest neighbor triplets (\texttt{n\_outliers}), \(3\) random triplets
per point (\texttt{n\_random}) is used as the NLDR method. The model is
generated with \(103\) bins, which have a width of \(0.154\) and a
height of \(0.133\). Edges with lengths greater than \(0.266\) are
removed.

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_best_trimap_trimesh.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_trimap_best_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_trimap_best_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_trimap_best_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc-best}Model in \gD{}, on the TriMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has twists. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \url{https://youtu.be/zEz2MUCtADM}).}

>>>>

\caption{\label{fig-scurve-true-sc}Three views of the true model in
projections from \(7\text{-}D\), for the S-curve data. The model closely
fits the shape. (The \textbf{langevitour} software is used to view the
data with a tour, and the full video is available at
\url{https://youtu.be/tYATMiSlCXQ}).}

@@

@@

@@
